Draft

### 2020-10-14 Final.Rmd
thesis v3 changes (before due date 18 Oct)

---
compact-title: no
editor_options:
  chunk_output_type: console
  header-includes:
  - \usepackage{amsmath}
  - \usepackage{setspace}\doublespacing
  - \usepackage[hyphens]{url}
  - \usepackage{boondox-cal}
fontsize: 12pt
geometry: margin=1in
output:
  pdf_document:
    fig_height: 3.5
    fig_width: 4.5
link-citations: yes
bibliography: references.bib
---

@@

With correct model specification being a major challenge for conventional likelihood-based prediction, scoring rules have been used to produce forecasts that are accurate – in a well-defined sense - in the presence of misspecification. Building off previous research, this paper conducts numerical and empirical analyses to explore the impact of the form and degree of model misspecification on probabilistic forecasts that are optimal under a given score. In particular, we assess the predictive performance of optimal forecasts in two empirical contexts: prediction of the Value-at-Risk and prediction of the VIX Volatility Index. Results show that the greater the degree of model misspecification, the more beneficial is optimal prediction, no matter which form of model misspecification is. Predictions that are optimal according to the censored likelihood score that rewards predictive accuracy in a tail are substantially more accurate at predicting extreme events in said tail than the alternatives, including likelihood-based predictions.

@@

Probabilistic forecasts can provide complete information about future uncertainty, which can be more valuable than point and interval forecasts to forecasters. However, previous approaches to prediction - including probabilistic methods – typically assume that the predictive model or the likelihood function correctly specifies the true data generating process (DGP) or the true DGP lies in the model pools, which is almost certainly untrue in practice. Optimal probabilistic forecasting refers to the construction of a predictive probability distribution that is optimal according to a user-specified proper scoring rule [@optimal]. It is not constructed based on the conventional likelihood function but on a proper scoring rule that matches the specific problem at hand. Optimal probabilistic forecasts aim to improve the predictive accuracy of a misspecified model, whilst the conventional approaches to probabilistic forecasting focus on the development of increasingly less misspecified models that can potentially yield better probabilistic forecasts.

A variety of proper scoring rules allows users to produce probabilistic predictions that are designed to perform well according to the forecasting metric that is important to the problem at hand [@gneiting2007]. Some recent research shows that forecasts produced using a given scoring rule can yield better out-of-sample accuracy - measured by that scoring rule - than conventional likelihood-based forecasts, in particular in the presence of model misspecification; see @opschoor2017, @fbp2019 and @optimal. Among all these investigations, it is the censored likelihood score (CLS) proposed originally by @diks2011, that captures our attention for the purpose of demonstrating the application of optimal probabilistic forecasts in finance. Its ‘focusing’ feature has great potential in financial risk management. In other words, CLS allows a forecaster to focus on predicting any particular region of interest more accurately. Therefore, its usage in this context represents an important contribution to risk prediction in financial settings.

Whilst some empirical investigations about the performance of optimal forecasts were undertaken in @optimal, these were primarily illustrative, and left much scope for exploring the performance of optimal probabilistic forecasting methods in forecasting different types of financial measures, and under different assumed models.

This research paper extends the work of @optimal by investigating the effect of the form and degree of model misspecification on the performance of optimal probabilistic forecasts in financial settings; in particular by conducting empirical analyses of how optimal forecasts perform in predicting the Value-at-Risk (VaR) and the VIX Volatility Index (VIX). Importantly, the empirical dataset used extends over a period of time that precedes the 2008 global financial crisis (GFC) and that includes the latest period in which COVID-19 has had an impact on financial markets.

The paper proceeds as follows. Section 2 explains the basic idea about how scoring rules are applied in producing and evaluating density forecasts, and provides the definitions of some commonly used scoring rules. Section 3 focuses on investigating the effects of different forms and degrees of model misspecification on the performance of optimal forecasts, using data simulated from the (generalized) autoregressive conditional heteroscedasticity ((G)ARCH) and inversion copula models. The assumed predictive model is fixed as ARCH(1) for the purpose of manipulating the degree of model misspecification. Although the simulation design is introduced in this section, it forms the foundation of methodologies used in all experiments conducted in other sections of this paper. In Section 4, we emulate the simulation exercise on an empirical example for financial returns of the S&P 500 index, including the prediction of the Value-at-Risk (VaR). The results illustrate the practical contributions to financial risk management. The empirical analysis of the VIX is provided in Section 5, where the predictive model is the heterogeneous autoregressive-realized volatility (HAR-RV) model with different error term specifications. We conclude and discuss any possible caveats in Section 6.

@@

Scoring rules are a type of criterion function that can be optimized to produce an optimal estimator and thus, a probabilistic prediction derived from this optimal estimator and an assumed model. They also play the role of encouraging forecasters to make careful and honest assessments in elicitation of subjectivist Bayesians, and evaluating and ranking competitive probabilistic forecasts, based on the predictive distribution and materialized events or values, by assigning a numerical score [@waite2005; @gneiting2007]. Therefore, the crucial importance of the propriety of scoring rules must be emphasized for their usage because improper scoring rules will assign a higher average score to an incorrect density forecast [@gneiting2007]. Consequently, forecasts based on improper scoring rules will not be ‘optimal’.

Suppose P and Q are predictive distributions and Q is the best forecast given all the available information. S(P,Q) denotes the expected value of S(P,$\cdot$) under Q. A scoring rule is said to be proper if $S(Q,Q) \geq S(P,Q)$ for all P and Q, and is strictly proper if $S(Q,Q) = S(P,Q)$ only happens when P = Q [@gneiting2007].

In terms of producing probabilistic forecasts, scoring rules can replace the conventional likelihood function in frequentist and Bayesian predictions; see @fbp2019 and @optimal. Supposing the scoring rule is positively oriented, then an estimator $\hat \theta$ obtained by maximizing a scoring rule $S(\theta)$ is said to be 'optimal' based on this scoring rule. 
\begin{equation} \label{eq:1}
\hat \theta =arg \max_\theta S(\theta)
\end{equation}
Under certain conditions, including that the scoring rule is 'proper', $\hat \theta \to \theta_0 \ as \ \mathcal{T} \to \infty$,
where $\theta_0$ is the true parameter value and $\mathcal{T}$ is the total sample size of a time series variable $y_t$. The predictive distribution based on this optimal estimator, $p(y_{T+1}|M,\hat \theta,y_{1:T})$, has been produced from the assumed model by optimizing a proper scoring rule. ^[M refers to the assumed model and it is omitted in the following notation for simplicity, since the assumed model does not change.]

In addition, in terms of evaluating predictions, scoring rules assign numerical values to density forecasts, addressing both sharpness and calibration simultaneously. It is usually the average score ($\bar S$) that is used to directly compare predictive accuracy among predictions produced by optimizing different scoring rules [@gneiting2007]. 
\begin{equation} \label{eq:sbar}
\bar S = \frac{1}{T}\sum_{t=1}^T S(p_{t+1},y_t)
\end{equation}
For a positively oriented score, for example, a higher value will be assigned to a better forecast between two competing candidates, on the condition of the scoring rule being proper.

@@

A variety of scoring rules have been developed to tackle different problems. Some commonly used proper scoring rules are adopted in the analyses in this paper, such as the logarithmic score (LS), the continuously ranked probability score (CRPS) and the censored likelihood score (CLS).

The logarithmic score is defined as in $\eqref{eq:ls}$ where $p_t$ is the predictive density. 
\begin{equation} \label{eq:ls}
S_{LS}(p_{t-1}, y_t) = log[p_{t-1}(y_t)]
\end{equation}
It is a local strictly proper scoring rule, which means it will assign a higher score to the correct probabilistic forecast, and it is superior to quadratic and spherical scoring rules when the rank ordering is important or the impact of the nonlinear utility function used is a concern for forecasters [@bickel2007]. One common usage of the logarithmic score in frequentist econometrics is the maximum likelihood estimation (MLE).
\begin{equation} \label{eq:mle}
\hat \theta_{MLE}=arg \max_\theta \{log[p_{t-1}(y_t|\theta)]\}
\end{equation}
It provides an asymptotically optimal and efficient estimation under the correctly specified log-likelihood function and regularity.

However, the logarithmic score is criticized for its unboundedness and its local property. @bernardo1979 states "locality requires the utility of probabilistic influence to depend only upon the probability density of the true state". @gneiting2007 also argue that the logarithmic score is insensitive to distance and will not reward predictions that are close to but not identical to the materialized event. @gneiting2007 propose the continuously ranked probability score, which is sensitive to distance and is defined as in $\eqref{eq:crps}$ 
\begin{equation} \label{eq:crps}
CRPS(P_{t-1},x_t)=-\int_{-\infty}^{\infty}[P_{t-1}(y)-I(y\geq x_t)]^2dy
\end{equation}
where $\mathcal{P}$ is the cumulative distribution function, *I* is the indicator function, and $x_t$ is the materialized event.

The formula can be simplified to $\eqref{eq:crnorm}$ if the prediction distribution is Gaussian with mean $\mu$ and variance $\sigma^2$.
\begin{equation} \label{eq:crnorm}
CRPS(N_{t-1},x_t)=\sigma[\frac{1}{\sqrt{\pi}}-2\phi(\frac{x_t-\mu}{\sigma})-\frac{x_t-\mu}{\sigma}(2\Phi(\frac{x_t-\mu}{\sigma})-1)]
\end{equation}
where $\phi$ and $\Phi$ are the probability density function and cumulative distribution function of the standard Gaussian distribution.

Both LS and CRPS are used for producing predictive densities and evaluating the out-of-sample predictive performance. In terms of accurately predicting a certain region of a distribution, they are typically used together with weighted likelihood [@gneiting2011]. @diks2011 propose the censored likelihood score, which allows users to assess forecasts only on a region (regions) of interest instead of using weights to emphasize a particular part of the entire density forecast. Moreover, it can be easily used to combine density forecasts and yield better predictive accuracy. It is defined as in $\eqref{eq:cls}$
\begin{equation} \label{eq:cls}
S_{CLS}(p_{t-1}, y_t)=I(y_{t} \in A_t)log[ p_{t-1}(y_{t})]+I(y_{t} \in A_t^c)log[\int_{A_t^c} p_{t-1}(s)ds]
\end{equation}
where $p_t$ is the predictive probability density function, $A_t$ is the region of interest and $A_t^c$ is the complement of $A_t$. @opschoor2017 prove that weighted density forecasts based on optimizing CLS outperform those on LS and CRPS.

@@

Optimal forecasts can outperform predictions produced by conventional methods out of sample; see @opschoor2017, @fbp2019 abd @optimal; but the underlying reasons driving this phenomenon are still under investigation. Recent research show that the degree of model misspecification impacts the performance of optimal forecasts. The greater the degree of misspecification is, the more benefits are gained from optimal forecasts in both Bayesian and frequentist predictions, conditional on the assumed predictive model being compatible; see [@fbp2019] and [@optimal]. The simulation analysis in this paper will extend the exploration in this field and ask the question ‘Will the performance of optimal forecasts change when a different form of misspecification occurs?’.

In order to set the scene for the financial application analyses in following sections of this paper, we simulate a time series variable $y_t$ that mimics the behavior of financial returns and their volatility. Specific simulation scenarios are listed in Table 1 ($t_\nu$ indicates a Student-t distribution with $\nu$ degrees of freedom).

\begin{table}[!ht]
\centering
\resizebox{\textwidth}{!}{
\begin{tabular}{|c|c|c|c|}
\hline
\multicolumn{4}{|c|}{\textbf{Table 1: Simulation design}} \\ \hline
          & \textbf{Scenario (i)} & \textbf{Scenario (ii)} & \textbf{Scenario (iii)} \\ \hline
\textbf{True DGP} & $y_t = \sigma_t \epsilon_t$ & $y_t = \sigma_t \epsilon_t$ & Stochastic volatility inversion copula \\
& $\sigma_t^2 = 1 + 0.2y_{t-1}^2+0.7\sigma_{t-1}^2$ & $\sigma_t^2 = 1 + 0.2y_{t-1}^2+0.7\sigma_{t-1}^2$ & Shape parameter = \{0, -3, -5\} \\ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim (\frac{\nu-2}{\nu})^{0.5} * t_\nu$ & \\ & & $\nu \in \{3,12\}$ & \\ \hline

\textbf{Assumed model} & $y_t = \mu +\sigma_t \epsilon_t$ & $y_t = \mu +\sigma_t \epsilon_t$ & $y_t = \mu +\sigma_t \epsilon_t$ \\ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$ \\ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$ \\ \hline
\end{tabular}}
\caption{It shows three simulation scenarios conducted in the numerical analysis sections where Scenario (i) shows the correct model specification, Scenario (ii) shows that the true DGP is GARCH with Student-t distribution while the assumed model creates normal distribution, and Scenario (iii) creates an asymmetric true DGP, while the assumed model can only produces symmetric predictive distribution.}
\end{table}

GARCH models are used to capture the volatility clustering and serial dependence usually observed in empirical stock returns, and the negative marginal skewness will be incorporated by using a stochastic volatility inversion copula model, with the degree of marginal skewness controlled by the shape parameter.

Copula models are a flexible approach to represent the joint distribution function of a set of variables [@fan2014]. In recent years, these models have been applied for modelling of serial dependence as shown in $\eqref{eq:copula}$ [@inversion2018]. 
\begin{equation} \label{eq:copula}
p_{t-1}(y_t)=c(P(y_t),P(y_{t-1}))p(y_{t-1})
\end{equation}
where $\mathcal{P}()$ and $\mathcal{p}$ denote the marginal distribution and density function of $y_t$ respectively, and c() is the copula density function that captures the dependence between $y_t$ and $y_{t-1}$.

For the simulation exercise, the marginal distribution $\mathcal{P}()$ is chosen to be the standard skew-normal distribution, while c() is chosen to be the inversion copula of the stochastic volatility model described in @inversion2018. The stochastic volatility inversion copula model used in this section allows us to keep the dependence structure of a state space model and provides the flexibility of using an asymmetric marginal distribution that is often observed in financial returns [@inversion2018].

@@

We apply the scoring rules introduced in Section 2.2 and set CLS to focus on 10%, 20%, 80% and 90% tails of the empirical marginal distribution, corresponding to the risks of long and short portfolios of financial investments, and we label them as CLS10, CLS20, CLS80 and CLS90 in following tables and figures. Due to the fact that there is no reliable estimate of the true conditional densities, only the tails of the marginal distributions are set to be the standard when assessing the predictive accuracy by CLS, rather than the conditional distributions. Meanwhile, MLE is included as a benchmark for comparing whether optimal forecasts can provide benefits or not, since MLE is asymptotically optimal and efficient under the correct model specification and regularity. Even though this property does not hold under misspecification, MLE can still give insights about how conventional likelihood-based methods perform.

We conduct Monte Carlo simulations using the methodology in @optimal and @fbp2019. Specific steps are as follows:

Let $P^{t-1}_{\boldsymbol{\hat \theta_1^{[i]}}}$ be the one-step-ahead predictive distribution function based on the assumed model and optimized according to the scoring rule $S_i$, and $p(y_t|\mathcal{F}_{t-1},\boldsymbol{\theta})$ be the corresponding predictive density function at time $\mathcal{t}$.

  1.	Generate T = 6000 observations for $y_t$ from the true DGP

  2.	Use $y_{1:1000}$ to estimate $\boldsymbol{\hat \theta}^{[i]}$ in the assumed predictive model based on the positively oriented score $S_i$ where $\boldsymbol{\hat \theta}^{[i]} = \{\hat \mu, \hat \alpha_0, \hat \alpha_1\}^{[i]}$

\begin{equation} \label{eq:theta}
\boldsymbol{{\hat \theta}^{[i]}}:=arg\max_{\boldsymbol{\theta \in \Theta}}\bar S_i({\boldsymbol\theta})
\end{equation}
\begin{equation} \label{eq:score}
\bar S_i(\boldsymbol\theta):=\frac{1}{T-(\tau+1)}\sum^{T-\tau}_{t=2}S_i(P_{\boldsymbol\theta}^{t-1},y_t)
\end{equation}
  3.	Produce the one-step-ahead predictive $P^{t-1}_{\boldsymbol{\hat \theta_1^{[i]}}}$, and compute the out-of-sample score using $S_j$, where $S_i$ and $S_j$ refer to $\eqref{eq:LS}$ $\eqref{eq:CRPS}$ $\eqref{eq:CLS}$:^[The CRPS in $\eqref{eq:CRPS}$ is transformed to a positively-oriented score for the purpose of convenient comparison among all scores.]

>>>>

---
compact-title: no
editor_options:
  chunk_output_type: console
  header-includes:
  - \usepackage{amsmath}
  - \usepackage{amsfonts}
  - \usepackage{setspace}\doublespacing
  - \usepackage[hyphens]{url}
  - \usepackage{float}
fontsize: 12pt
geometry: margin=1in
output:
  pdf_document:
    fig_height: 3.5
    fig_width: 4.5
link-citations: yes
bibliography: references.bib
---

@@

With correct model specification being a major challenge for conventional likelihood-based prediction, scoring rules have been used to produce forecasts that are accurate – in a well-defined sense - in the presence of misspecification. Building on previous research, this paper conducts numerical and empirical analyses to explore the impact of the form and degree of model misspecification on probabilistic forecasts that are optimal under a given score. In particular, we assess the predictive performance of optimal forecasts in two empirical contexts: prediction of the Value-at-Risk of a financial return and prediction of the VIX volatility index. Results show that the greater the degree of model misspecification, the more beneficial is optimal prediction, no matter what the form of model misspecification. Most notably, predictions that are optimal according to the censored likelihood score, which rewards predictive accuracy in a tail are substantially more accurate at predicting extreme events in said tail than the alternatives, including likelihood-based predictions.

@@

Probabilistic forecasts can provide complete information about future uncertainty, which can be more valuable to forecasters than point and interval forecasts. However, previous approaches to prediction - including probabilistic methods – typically assume that the predictive model, or the likelihood function, correctly specifies the true data generating process (DGP) or that the true DGP lies in a specified set of models, which is almost certainly untrue in practice. Optimal probabilistic forecasting refers to the construction of a predictive probability distribution that is optimal according to a user-specified proper scoring rule [@optimal]. It is not based on the conventional likelihood function but on a proper scoring rule that matches the specific problem at hand. Optimal probabilistic forecasts aim to yield accurate predictions in the presence of a misspecified predictive model, whilst the conventional approaches to probabilistic forecasting are tied more closely to the predictive model, and are only as accurate as that model itself.

Particular proper scoring rules allow users to produce probabilistic predictions that are designed to perform well according to the forecasting metric that is important to the problem at hand [@gneiting2007]. Some recent research shows that forecasts produced using a given scoring rule can yield better out-of-sample accuracy - measured by that scoring rule - than conventional likelihood-based forecasts, in particular in the presence of model misspecification; see @opschoor2017, @fbp2020 and @optimal. Among all these investigations, it is the censored likelihood score (CLS) proposed originally by @diks2011, that captures our attention for the purpose of demonstrating the application of optimal probabilistic forecasts in finance. Its ‘focusing’ feature has great potential in financial risk management. In other words, CLS allows a forecaster to focus on predicting any particular region of interest accurately. Therefore, its use in this context represents an important contribution to risk prediction in financial settings.

Whilst some empirical investigations of the performance of optimal forecasts were undertaken in @optimal, these were primarily illustrative, and left much scope for exploring the performance of optimal probabilistic forecasting methods in forecasting different types of financial measures, and under different assumed models. This research paper extends the work of @optimal by investigating the effect of the form and degree of model misspecification on the performance of optimal probabilistic forecasts in financial settings; in particular by conducting empirical analyses of how optimal forecasts perform in predicting the Value-at-Risk (VaR) and the VIX volatility index (VIX). Importantly, the empirical dataset used extends over a period of time that precedes the 2008 global financial crisis (GFC) and that includes the latest period in which COVID-19 has had an impact on financial markets.

The paper proceeds as follows. Section 2 explains the basic idea about how scoring rules are applied in producing and evaluating density forecasts, and provides the definitions of some commonly used scoring rules. Section 3 focuses on investigating the effects of different forms and degrees of model misspecification on the performance of optimal forecasts, using data simulated from the (generalized) autoregressive conditional heteroscedasticity ((G)ARCH) and inversion copula models. The assumed predictive model is fixed as a Gaussian ARCH(1) model for the purpose of controlling the degree of model misspecification. In Section 4, we emulate the simulation exercise in an empirical example for financial returns on the S&P 500 stock index, including the prediction of the VaR. The results illustrate the practical contributions of our predictive approach to financial risk management. The empirical analysis of the VIX is provided in Section 5, where the predictive model is the heterogeneous autoregressive-realized volatility (HAR-RV) model with different error term specifications. We conclude and discuss any possible caveats in Section 6.

@@

Scoring rules $S(\cdot,\cdot)$ are a type of criterion function that can be optimized to produce an optimal estimator and hence, a probabilistic prediction derived from this optimal estimator. They also play the role of evaluating and ranking competing probabilistic forecasts, based on materialized events or values, by assigning a numerical score [@gneiting2007]. That is, if the forecaster produces a predictive distribution $\mathit{P}$ and the event $y$ materializes, then the reward to this prediction given by a scoring rule is denoted by $S(P,y)$. For a positively-oriented score, a higher value will be assigned to a better forecast between two competing candidates, on the condition of the scoring rule being proper. The propriety of the scoring rule is crucial here, as an improper scoring rule may assign a higher average score to an incorrect density forecast [@gneiting2007]. Consequently, only proper scoring rules are used in the production of optimal forecasts.

Suppose $P$ is the predictive distribution and $Q_0$ is the true DGP. $\mathbb{S}(P,Q_0)$ denotes the expected score of $S(P,\cdot)$ under $Q_0$. That is,
\begin{equation} \label{eq:score}
\mathbb{S}(P,Q_0)=\int_{y \in \Omega}S(P,y)dQ_0(y)
\end{equation}
where $\Omega$ is a probability space. 
A scoring rule is said to be proper if $\mathbb{S}(Q_0,Q_0) \geq \mathbb{S}(P,Q_0)$ for all $P$ and $Q_0$, and is strictly proper if $\mathbb{S}(Q_0,Q_0) = \mathbb{S}(P,Q_0)$ only when $P = Q_0$ [@gneiting2007]. This ensures that a proper scoring rule is maximized when the prediction reveals the truth, on the condition that the predictive distribution class $\mathcal{P}$ contains $Q_0$.

However, in practice, the expected score $\mathbb{S}(\cdot,Q_0)$ is unknown and cannot be obtained, but we can use a sample average $\bar S(\cdot)$ as a reasonable estimation. Asymptotically, the true predictive distribution can be recovered by optimizing a sample criterion of any proper scoring rule, if the true predictive is contained in the predictive class over which the maximization occurs. Even when $Q_0$ is not contained in the predictive distribution class $\mathcal{P}$ proposed by the forecaster, it does not change the fact that a proper scoring rule will reward a particular form of forecast accuracy and hence, select the best forecast within the proposed predictive distribution class, according to this scoring rule.

Assume the scoring rule is positively-oriented and the unknown parameters of the assumed predictive model are denoted as $\boldsymbol \theta \in \Theta$, and let $P^{t-1}_{\boldsymbol{\theta}}$ := $P(\cdot|\mathcal{F}_{t-1},\boldsymbol \theta)$ be the one-step-ahead predictive distribution function based on the assumed model where $\mathcal{F}_{t-1}$ represents all the information available at time $t-1$, and $p^{t-1}_{\boldsymbol{\theta}}$ := $p(\cdot|\mathcal{F}_{t-1},\boldsymbol \theta)$ be the corresponding predictive density function at time $t$. 
Then an estimator $\boldsymbol{\hat \theta}$ obtained by maximizing $\bar S(\boldsymbol{\theta})$ is said to be 'optimal' based on this scoring rule and $P^{t-1}_{\boldsymbol{\hat \theta}}$ is referred to as the optimal predictive. 
Specifically, we define 
\begin{equation} \label{eq:1}
\boldsymbol{\hat \theta} =arg \max_{\boldsymbol{\theta} \in \Theta} \bar S(\boldsymbol{\theta})
\end{equation}
where 
\begin{equation} \label{eq:sbar}
\bar S = \frac{1}{T-\tau+1}\sum_{t=2}^{T-\tau} S(P_{\boldsymbol{\theta}}^{t-1},y_t)
\end{equation}
with $\mathit{T}$ the total number of observations on a time series variable $y_t$ and $\tau$ the out-of-sample size. Under certain conditions, including that the scoring rule is proper and that the predictive model is correctly specified, $\boldsymbol{\hat \theta} \to \boldsymbol{\theta}_0 \ as \ \mathit{T} \to \infty$ where $\boldsymbol{\theta}_0$ represent the true (vector) parameter.

@@

A variety of scoring rules have been developed to tackle different problems. Some commonly used proper scoring rules are adopted in the analyses in this paper, such as the logarithmic score (LS), the continuously ranked probability score (CRPS) and the CLS.

The LS is defined as
\begin{equation} \label{eq:ls}
S_{LS}(P^{t-1}_{\boldsymbol \theta}, y_t) = ln[p(y_t|\mathcal{F}_{t-1},\boldsymbol{\theta})]
\end{equation}
where $p(\cdot|\mathcal{F}_{t-1},\boldsymbol{\theta})$ is the predictive density function. It is a local strictly proper scoring rule, which means it will assign a higher score to the correct probabilistic forecast, and it is superior to quadratic and spherical scoring rules when the rank ordering is important or the impact of the nonlinear utility function used is a concern for forecasters [@bickel2007]. One common usage of the LS in frequentist econometrics is maximum likelihood estimation (MLE). That is, 
\begin{equation} \label{eq:mle}
\boldsymbol{\hat \theta}_{MLE}=arg \max_{\boldsymbol{\theta} \in \Theta} \{\frac{1}{T} \sum_{t=1}^T ln[p(y_t|\mathcal{F}_{t-1},\boldsymbol \theta)]\}
\end{equation}
LS yields an asymptotically efficient estimator of $\boldsymbol \theta$ under correct specification and regularity.

However, the LS is criticized for its unboundedness and its local property. @bernardo1979 states "locality requires the utility of probabilistic influence to depend only upon the probability density of the true state". @gneiting2007 also argue that the LS is insensitive to distance and will not reward predictions that are close to but not identical to the materialized event. @gneiting2007 propose the continuously ranked probability score, which is sensitive to distance and is defined as
\begin{equation} \label{eq:crps}
S_{CRPS}(P^{t-1}_{\boldsymbol \theta},y_t)=-\int_{-\infty}^{\infty}[P(y|\mathcal{F}_{t-1},\boldsymbol{\theta})-I(y\geq y_t)]^2dy
\end{equation}
where $\mathit{P}(\cdot|\mathcal{F}_{t-1},\boldsymbol{\theta})$ is the predictive cumulative distribution function, *I* is the indicator function, and $y_t$ is the materialized event.

The formula can be simplified as follows if the predictive distribution is Gaussian with mean $\mu$ and variance $\sigma^2$, 
\begin{equation} \label{eq:crnorm}
S_{CRPS}(N^{t-1}_{\boldsymbol \theta},y_t)=\sigma[\frac{1}{\sqrt{\pi}}-2\phi(\frac{y_t-\mu}{\sigma})-\frac{y_t-\mu}{\sigma}(2\Phi(\frac{y_t-\mu}{\sigma})-1)]
\end{equation}
where $\phi$ and $\Phi$ are the probability density function and cumulative distribution function of the standard Gaussian distribution.

Both LS and CRPS are used for producing predictive densities and evaluating the out-of-sample predictive performance. In terms of accurately predicting a certain region of a distribution, they are typically used together with weighted likelihood [@gneiting2011]. @diks2011 propose the CLS, which allows users to reward forecasts only on a region (regions) of interest instead of using weights to emphasize a particular part of the entire density forecast. Moreover, it can be easily used to combine density forecasts and yield better predictive accuracy. It is defined as
\begin{equation} \label{eq:cls}
S_{CLS}(P^{t-1}_{\boldsymbol \theta}, y_t)=I(y_{t} \in A)ln p(y_{t}|\mathcal{F}_{t-1},\boldsymbol{\theta})+I(y_{t} \in A^c)ln[\int_{A^c} p(y|\mathcal{F}_{t-1},\boldsymbol{\theta})dy]
\end{equation}
where $p(\cdot|\mathcal{F}_{t-1},\boldsymbol{\theta})$ is the predictive probability density function, $A$ is the region of interest and $A^c$ is the complement of $A$. @opschoor2017 prove that weighted density forecasts based on optimizing CLS outperform those on LS and CRPS.

@@

Optimal forecasts can outperform predictions produced by conventional methods out-of-sample; see @opschoor2017, @fbp2020 abd @optimal; but the underlying reasons driving this phenomenon are still under investigation. Recent research show that the degree of model misspecification impacts the performance of optimal forecasts. The greater the degree of misspecification is, the more benefits are gained from optimal forecasts in both Bayesian and frequentist predictions, conditional on the assumed predictive model being broadly 'compatible' with the true DGP; see @fbp2020 and @optimal. The simulation analysis in this paper will extend the exploration in this field and ask the question ‘Will the performance of optimal forecasts change when a different form of misspecification occurs?’.

In order to set the scene for the financial application analyses in the following sections of this paper, we simulate a time series variable $y_t$ that mimics the behavior of financial returns and their volatility. Specific simulation scenarios are listed in Table 1 ($t_\nu$ indicates a Student-t distribution with $\nu$ degrees of freedom).

*Table 1: The three simulation scenarios used in the numerical analysis. Scenario (i) represents correct model specification; Scenario (ii) represents a form of misspecification where the true DGP is GARCH with Student-t distribution while the assumed model is Gaussian ARCH(1); Scenario (iii) represents a more extreme form of misspecification, where the true DGP is an stochastic volatility model with a non-Gaussian marginal distribution while the assumed model is Gaussian ARCH(1).*

\begin{table}[H]
\centering
\resizebox{\textwidth}{!}{
\begin{tabular}{|c|c|c|c|}
\hline
\multicolumn{4}{|c|}{\textbf{Table 1: Simulation design}} \\ \hline
          & \textbf{Scenario (i)} & \textbf{Scenario (ii)} & \textbf{Scenario (iii)} \\ \hline
\textbf{True DGP} & $y_t = \sigma_t \epsilon_t$ & $y_t = \sigma_t \epsilon_t$ & Stochastic volatility inversion copula \\
& $\sigma_t^2 = 1 + 0.2y_{t-1}^2$ & $\sigma_t^2 = 1 + 0.2y_{t-1}^2+0.7\sigma_{t-1}^2$ & Shape parameter = \{0, -3, -5\} \\ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim (\frac{\nu-2}{\nu})^{0.5} * t_\nu$ & \\ & & $\nu \in \{3,12,35\}$ & \\ \hline

\textbf{Assumed model} & $y_t = \mu +\sigma_t \epsilon_t$ & $y_t = \mu +\sigma_t \epsilon_t$ & $y_t = \mu +\sigma_t \epsilon_t$ \\ & $\sigma_t^2 = \alpha_0 + \alpha_1 y_{t-1}^2$ & $\sigma_t^2 = \alpha_0 + \alpha_1 y_{t-1}^2$ & $\sigma_t^2 = \alpha_0 + \alpha_1 y_{t-1}^2$ \\ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$ \\ \hline
\end{tabular}}
\end{table}

GARCH models are used to capture the volatility clustering and serial dependence that are usually observed in empirical stock returns, and the negative marginal skewness will be incorporated by using a stochastic volatility inversion copula model, with the degree of marginal skewness controlled by the shape parameter.

Copula models are a flexible way of representing the joint distribution function of a set of variables [@fan2014]. In recent years, these models have been applied to modelling serial dependence, which can be constructed as: 
\begin{equation} \label{eq:copula}
p_{t-1}(y_t)=c(P(y_t),P(y_{t-1}))p(y_{t-1})
\end{equation}
where $\mathit{P}()$ and $\mathit{p}$() denote the marginal distribution and density function of $y_t$ respectively, and c() is the copula density function that captures the dependence between $y_t$ and $y_{t-1}$.

For the simulation exercise, the marginal distribution $\mathit{P}()$ is chosen to be the standard skew-normal distribution, while c() is chosen to be the inversion copula of the stochastic volatility model described in @inversion2018. The stochastic volatility inversion copula model allows us to keep the dependence structure of a state space model and provides the flexibility of using an asymmetric marginal distribution that is often observed in financial returns [@inversion2018].

@@

We apply the scoring rules introduced in Section 2.2 and set CLS to focus on the 10%, 20%, 80% and 90% tails of the empirical marginal distribution, corresponding to the risks of long and short portfolios of financial investments, and we label them as CLS10, CLS20, CLS80 and CLS90 in the following tables and figures. Due to the fact that there is no reliable estimate of the true conditional densities, only the tails of the marginal distributions are set to be the standard when assessing the predictive accuracy by CLS, rather than the conditional distributions. Meanwhile, LS gives insights about the performance of the conventional likelihood-based methods and is used as a benchmark for comparing whether optimal forecasts can provide benefits or not.

We conduct Monte Carlo simulations using the methodology in @optimal and @fbp2020. Specific steps are as follows:

Let $P^{t-1}_{\boldsymbol{\hat \theta^{[i]}}}$ be the one-step-ahead predictive distribution function based on the Gaussian ARCH(1) model and optimized according to the scoring rule $S_i$, and $p(y_t|\mathcal{F}_{t-1},\boldsymbol{\hat \theta^{[i]}})$ be the corresponding predictive density function at time $\mathit{t}$.

  1.	Generate T = 6000 observations of $y_t$ from the true DGP

  2.	Use observations $y_t$ where $t = 1,2,...,1000$ to estimate $\boldsymbol{\hat \theta}^{[i]} = \{\hat \mu, \hat \alpha_0, \hat \alpha_1\}^{[i]}$ as in $\eqref{eq:1}$ based on $S_i$, $i \in \{LS, CRPS, CSL10,CSL20,CSL80,CSL90\}$ where $S_i$ refers to $\eqref{eq:ls}$ $\eqref{eq:crps}$ $\eqref{eq:cls}$

  3.	Produce the one-step-ahead predictive $P^{t-1}_{\boldsymbol{\hat \theta^{[i]}}}$, and compute the out-of-sample score $S_j$, $j \in \{LS, CRPS, CSL10,CSL20,CSL80,CSL90\}$
where $S_j$ refers to $\eqref{eq:ls}$ $\eqref{eq:crps}$ $\eqref{eq:cls}$:^[The CRPS in $\eqref{eq:crps}$ is transformed to a positively-oriented score for the purpose of convenient comparison among all scores.]

  4. Expand estimation window by one observation and repeat steps 2-3 with $\tau = T-1000$ times and compute the average scores:^[Out-of-sample size $\tau = 5000$ is sufficiently large to let the optimal forecasts take place; see @optimal for full discussion about sample size effects on optimal forecasts.]

\begin{equation} \label{eq:avgscore}
\bar S_j(\boldsymbol{\hat \theta^{[i]}})=\frac{1}{\tau}\sum^T_{t=T-\tau+1}S_j(P_{\boldsymbol{\hat \theta^{[i]}}}^{t-1},y_t)
\end{equation}
